Approximation as Differentiation

### 2025-04-16 appendix/notes/grothendieck.tex
Minor tweaks..

\noindent When $F$ is contravariant, a morphism $f: X \to Y$ is a morphism $\idx{f}: \idx{X} \to \idx{Y}$ in
$\cat{C}$ paired with a morphism $\faml{f}: \faml{X} \to F(\idx{f})(\faml{Y})$ in $F(\idx{X})$.

>>>>

\noindent When $F$ is contravariant, a morphism $f: X \to Y$ in $\Grothendieck{\cat{C}}{F}$ is a morphism
$\idx{f}: \idx{X} \to \idx{Y}$ in $\cat{C}$ paired with a morphism $\faml{f}: \faml{X} \to
F(\idx{f})(\faml{Y})$ in $F(\idx{X})$. \todo{Might want to unpack this a bit.}
